\documentclass[10pt]{iopart}
\input{setup}

\def\SI{Slimplectic Integrator}
\def\SymI{{Symplectic integrator}}
\newcommand{\autodiff}{automatic-differentiation}
\def\vbq{\vb{q}}
\newcommand{\orgimpl}{\textit{original implementation}}
\newcommand{\updimpl}{\textit{updated implementation}}
\newcommand{\Niter}{N_{\mathrm{iter}}}
\newcommand{\etall}{{\it et al.~\/}\ }
\newcommand{\ensquote}[1]{`{#1}'}

\begin{document}
\ioptwocol[{
\title{Iterations on the Slimplectic integrator and its applications to physically informed loss functions}
\author{J D Coles$^1$}
\address{$^1$ Department of Physics, University of Bath, Claverton Down, Bath BA2 7AY, UK}
\begin{abstract}
The Slimplectic Integrator developed by Tsang et al. [1] provided a new type of numerical integrator applicable to general non-conservative systems by applying the principle of stationary non-conservative action.

The Slimplectic Integrator introduced by Tsang et al. \cite{tsangSLIMPLECTICINTEGRATORSVARIATIONAL2015} provides fractional error bounds when integrating non-conservative systems. In this paper we present iterations on this method using modern computational techniques improving its computational performance by a factor of $\approx 10^4$, with a small fixed cost, for long-term integrations on the order of $\Niter \approx 10^6$ and orders $r < 40$. We present applications of this work to physically informed loss functions for identifying physical systems from observational data and use these in the training of a physics informed neural network to do this. This network, when trained, predicts Lagrangians that are accurate to an absolute RMS error of $\pm 5 \times 10^{-2}$ in $\vbq$ and $\pm 1 \times 10 ^{-1}$ in $\pi$.
\end{abstract}
}]

\input{1-intro-prelim.tex}
\input{2-method.tex}
\input{3-results-discussion.tex}

\ack

My gratitude is given to my project partner Aengus Roberts who was a guiding light when dealing with the complexities of neural networks, and who spent many hours designing, training and monitoring the network. Without him this would not have been possible. I would also like to thank Dr David Tsang for his constant support and discussion as we have moved through this project. 

\section*{References}
\bibliographystyle{iopart-num}
\bibliography{references,static}

\end{document}
